Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-10 2019/NUMTA_Barkalov/Special Issure/article.tex
Add some references

\usepackage{lineno,hyperref}
\usepackage[T1]{fontenc}
\modulolinenumbers[5]

@@

\cite{Evtushenko1971, Piyavskii1972, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019}.

>>>>

\usepackage{lineno,hyperref}
%\usepackage[T1]{fontenc}
\modulolinenumbers[5]

@@

\cite{Evtushenko1971, Piyavskii1972, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019, Kvasov2003, Sergeyev2010,Sergeyev2016, Horst1996, Gablonsky2001, Jones1993, Gaviano2003, Barkalov2018, Paulavicius2014, Sergeyev2015, Strongin2018,Gergel2017_2,Gergel2019}.
